---
title: "Working with config files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{working_with_config_files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Assume we are exloring some data set, and during our work, we've created a number 
of files with their specific structure.

```{r setup}
library(path.chain)
library(magrittr)

# Create an example file stucture
tmp <- create_temp_dir("files")
create_sample_dir(tmp, override = TRUE)

# Sample structure we've already created looks as follows
fs::dir_tree(tmp)
```

Then, we have two possible ways to represent this structure using `path.chain` package.

## 1. Using `full_path_chain` function, which returns a list of nested directories.
```{r possible.structures}
tmp <- create_temp_dir("files")
full.path.chain <- full_path_chain(tmp)

print(full.path.chain)

full.path.chain %>% 
  yaml::write_yaml(temp_path("config.yaml"))
```

Configurtion file **config.yaml** will look as follows:
```{yaml}
'.': files
data:
  '.': files/data
  example1.RData: files/data/example1.RData
  example2.RData: files/data/example2.RData
  persons.csv: files/data/persons.csv
docs:
  '.': files/docs
  schema.txt: files/docs/schema.txt
```

We can customize keys naming convention using `naming` argument.

```{r custom.naming.function}

naming_fun <- function(x){
  paste0("k", tools::file_path_sans_ext(stringi::stri_trans_totitle(basename(x))))
}

full.path.chain.2 <- full_path_chain(create_temp_dir("files"), "kRoot", naming_fun)

full.path.chain.2 %>% 
  yaml::write_yaml(create_temp_dir("config.yaml"))
```

```{yaml}
kRoot: files
kData:
  kRoot: files/data
  kExample1: files/data/example1.RData
  kExample2: files/data/example2.RData
  kPersons: files/data/persons.csv
kDocs:
  kRoot: files/docs
  kSchema: files/docs/schema.txt
```

If dir structure is not a only element in ou config file, we can wrap it with
some additional `list`.

```{r wrapped}
list(kDirs = full.path.chain.2) %>% 
  list(default = .) %>% 
  yaml::write_yaml(create_temp_dir("config.yaml"))
```

```{yaml}
default:
  kDirs:
    kRoot: files
    kData:
      kRoot: files/data
      kExample1: files/data/example1.RData
      kExample2: files/data/example2.RData
      kPersons: files/data/persons.csv
    kDocs:
      kRoot: files/docs
      kSchema: files/docs/schema.txt
```

Then, we can load such config file using `{config}` package:

```{r loading.full.path.config}
k.dirs <- config::get("kDirs", config = "default", file = create_temp_dir("config.yaml"))
k.dirs$kDocs$kRoot
k.dirs$kData$kExample1
```

What if we want to keep absolute paths rather than the relative ones?

```{r absolute.full.path}
full_path_chain(normalizePath(temp_path("files")), "kRoot", naming_fun) %>% 
  as_config("default", "kDirs") %>% 
  yaml::write_yaml(temp_path("config.yaml"))
```
Wrapping with **default** key is required by `config` package.

```{yaml}
default:
  kDirs:
    kRoot: /home/username/Desktop/myproject/files
    kData:
      kRoot: /home/username/Desktop/myproject/files/data
      kExample1: /home/username/Desktop/myproject/files/data/example1.RData
      kExample2: /home/username/Desktop/myproject/files/data/example2.RData
      kPersons: /home/username/Desktop/myproject/files/data/persons.csv
    kDocs:
      kRoot: /home/username/Desktop/myproject/files/docs
      kSchema: /home/username/Desktop/myproject/files/docs/schema.txt

```


## 2. Using `create_path_chain` function, which returns nested `path_chain` objects.

```{r path_chain}
path.chain <- create_path_chain(temp_path("files"), naming = naming_fun)

class(path.chain)

print(path.chain$kData$kExample1)

# Most verbose version
path.chain %>% 
  as.list(root.name = "kRoot") %>%
  as_config("default", "kDirs") %>% 
  yaml::write_yaml(temp_path("config.yaml"))

# Conciser
path.chain %>% 
  as_config("default", "kDirs", root.name = "kRoot") %>% 
  yaml::write_yaml(temp_path("config.yaml"))

```

```{yaml}
kDirs:
  kRoot: files/
  kData:
    kRoot: data/
    kExample1: kExample1
    kExample2: kExample2
    kPersons: kPersons
  kDocs:
    kRoot: docs/
    kSchema: kSchema
```

As you can see, such structur of the config file seems to be more legible than the one produced with
`full_path_chain` function. The config file shown above can be easily consumed using `config` package and `as_path_chain` function.

```{r as_path_chain}
k.dirs <- config::get("kDirs", "default", create_temp_dir("config.yaml")) %>% 
  as_path_chain()

class(k.dirs)

k.dirs$kData$.
k.dirs$kData$kExample1

```
